Inequalities Witnessing Quantum Incompatibility in The Triangle Scenario

### 2016-09-01 document/main.tex
add kbordermatrix.sty to repository, not automatic in ShareLatex. (The license of kbordermatrix.sty - lack of licensing information, to be precise - allows it to be on CTAN, but not in free software distributions.)
notational revamp

% === Commonly re-occurring symbols ===
\newcommand{\hgraph}{\mathcal{H}}
\newcommand{\graph}{\mathcal{G}}
\newcommand{\nodes}{\mathcal{N}}
\newcommand{\weights}{\mathcal{W}}
\newcommand{\edges}{\mathcal{E}}
\newcommand{\trans}{\mathcal{T}}
\newcommand{\ind}{\mathcal{I}}
\newcommand{\perm}{\Omega}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\ancestralindep}{\perp}
\newcommand{\valprod}{\circ}
% When I introduce a new term or definition
\newcommand{\term}[1]{\textcolor{Mahogany}{\textbf{#1}}}

% === Mathematical operators that are denoted with words ===
\newcommand{\setoperator}[1]{%
\expandafter\DeclareDocumentCommand\csname#1\endcsname{O{} O{} m}{{\mathsf{#1}_{##1}^{##2}\!}\br{##3}}%
}

\setoperator{Pa} % Parents of a node
\setoperator{Ch} % Children of a node
\setoperator{An} % Ancestry of a node
\setoperator{Sub} % subgraph
\setoperator{AnSub} % Ancestral subgraph
\setoperator{Ext} % Extension of outcomes
\setoperator{Com} % Compatible equivalence relation
\setoperator{Nec} % Necessary nodes
\setoperator{UnNec} % Unnecessary nodes
\setoperator{Inj} % injectable sets
\setoperator{ImInj} % images of the injectable sets
\setoperator{PreInj} % Pre-injectable sets
\setoperator{Aut} % graph automorphism
\setoperator{Orb} % Group Orbits
\setoperator{Perm} % Permutation group

\newcommand{\outc}[1]{o\!\bs{#1}} % Fritz's BBTII notation for observed outcomes
\DeclareDocumentCommand{\prob}{O{} O{}}{\ifthenelse{\equal{#1}{}}{P}{P_{#1}}\ifthenelse{\equal{#2}{}}{}{\!\br{#2}}} % probability distribution
\DeclareDocumentCommand{\probvec}{O{} O{}}{\ifthenelse{\equal{#1}{}}{\mathcal{P}}{\mathcal{P}_{#1}}\ifthenelse{\equal{#2}{}}{}{\!\br{#2}}} % probability distribution vector

@@

    \section{Introduction}
    \todo[TC]{Discuss why the marginal problem is important.}
    \section{Definitions \& Notation}
    \comment[TC]{This entire section should be integrated into the body when logical to do so.}
    \begin{definition}
        Borrowing the notation from \cite{Fritz_2014}, each random variable $v$ has a set of all possible outcomes called the \term{outcome space} or \term{valuation space} and is denoted $O_v$. When referencing a \textit{specific} element of $O_v$ or \textit{valuation} of $v$, the notation $\outc{v}$ is used. This notation generalizes to set of random variables $V = \bc{v_1, \ldots, v_{\abs{V}}}$;
        a specific outcome of $\outc{V} \in O_V$ is used to reference a particular tuple or vector of outcomes,
        \[ \outc{V} \defined \br{\outc{v_1}, \outc{v_2}, \ldots, \outc{v_{\abs{V}}} } = \br{\outc{v}}_{v \in V} \eq \label{eq:outcomespace}\]
        It is important to note that the ordering of events in \cref{eq:outcomespace} is irrelevant. Similarly, the outcome space $O_V$ for a set of random variables $V$ is the \term{valuation product} `$\valprod$' of the individual outcome spaces,
        \[ O_V \defined O_{v_1} \valprod \cdots \valprod O_{v_{\abs{V}}} \]
        Where `$\valprod$' is defined such that for $A \cap B = \emptyset$,
        \[ \outc{A} \valprod \outc{B} \defined \br{\outc{a_1}, \ldots, \outc{a_{\abs{A}}}, \outc{b_1}, \ldots, \outc{b_{\abs{B}}}} = \br{\outc{v}}_{v \in A \cup B} \]
        Often `$\valprod$' will be omitted where there is little ambiguity. When referencing the probability that a set of variables $V$ has outcome $\outc{V}$ (say $v_1 = 0, v_2 = 3$), we intend for the following class of notations to be used interchangeably.
        \[ \prob[V][\outc{V}] = \prob[][\outc{V}] = \prob[][\outc{v_1}\outc{v_2}] = \prob[][v_1 = 0, v_2 = 3] = \prob[][v_2 = 3, v_1 = 0] = \prob[v_1, v_2][03] \]
    \end{definition}

    \begin{definition}
        \label{def:extendable}
        An outcome $\outc{V}$ is said to be \term{extendable} to an outcome $\outc{W}$ (where $V \subseteq W$) if there exists an outcome $\outc{W\setminus V}$ such that $\outc{W} = \outc{W\setminus V} \valprod \outc{V}$.
        \[ \Ext{\outc{V} \to \outc{W}} \iff \exists \outc{W\setminus V} \mid \outc{W} = \outc{W\setminus V} \valprod \outc{V} \]
        The idea being that a \textit{less specific} outcome $\outc{V}$ can be made \textit{more specific} by assigning outcomes to the remaining random variables in $W \setminus V$. If such an outcome $\outc{W\setminus V}$ exists, it is unique.
    \end{definition}

    \begin{definition}
        The set of all extendable outcomes of $\outc{V}$ in $O_{W}$ is called the \term{extendable set} and can be written as,
        \[ \Ext[W]{\outc{V}} \defined \outc{V} \valprod O_{W\setminus V} \defined \bc{\outc{W} \in O_{W} \mid \Ext{\outc{V} \to \outc{W}}} \]
        The extendable set of $\outc{V}$ in $W$ is the set of all outcomes of $O_W$ that \textit{agree} with $\outc{V}$ about valuations for variables in $V$. In this language, two outcomes $\outc{V}$ and $\outc{W}$ are \term{compatible} if they are both extendable to some outcome $\outc{V \cup W}$. Equivalently, $\outc{V}$ and $\outc{W}$ agree on their valuations of $V \cap W$.
        \[ \Com{\outc{V}, \outc{W}} \iff \exists \outc{V \cup W} \mid \Ext{\outc{V} \to \outc{V \cup W}}, \Ext{\outc{W} \to \outc{V \cup W}} \]
    \end{definition}

    \begin{example}
        Consider two sets of random variables $V = \bc{a, b}$ and $W = \bc{a, b, c}$. Clearly $V \subseteq W$; a prerequisite for extendability. Also take all individual outcome spaces to be finite and of order 3: $O_a = O_b = O_c = \bc{1,2,3}$. Then $\outc{V} = \outc{\bc{a,b}} = \br{a = 1, b = 2}$ is extendable to the outcome $\outc{W} = \br{a = 1, b = 2, c = 1}$, and the extendable set of $\outc{V}$ in $O_{W}$ is,
        \[ \Ext[a,b,c]{a = 1, b = 2} = \bc{\br{a = 1, b = 2, c = 1}, \br{a = 1, b = 2, c = 2}, \br{a = 1, b = 2, c = 3}} \]
    \end{example}

@@

    \begin{definition}
        The \term{product distribution} two distributions is denoted as usual with $\times$ and is defined as,
        \[ \br{\prob[v] \times \prob[w]}\br{\outc{v}, \outc{w}} \defined \prob[v][\outc{v}]\prob[w][\outc{w}] \]
        A product distribution of $k$ distributions is defined recursively,
        \[ \prod_{i=1}^{k} \prob[v_i] \defined \br{\prob[v_1] \times \cdots \times \prob[v_k]} \]
    \end{definition}

    \begin{definition}
        The \term{marginalization} of a distribution $\prob[v \cup w]$ to the distribution $\prob[v]$ is denoted $\sum_{w} \prob[v \cup w] = \prob[v]$ and is defined such that,
        \[ \forall \outc{v} \in O_v : \br{\sum_{w} \prob[v, w]}\br{\outc{v}} \defined \sum_{o\bs{w} \in O_w} \prob[v, w][\outc{v}, \outc{w}] \]
    \end{definition}

    \begin{definition}
        Following common notation used in \cite{Fritz_2011}, we use the notation $\bs{k} = \br{1, \ldots, k}$ to be a finite index set. Moreover, when referencing a finite set with $k$ elements, we can write,
        \[ A_{\bs{k}} \defined \bc{A_i}_{i \in \bs{k}} = \bc{A_1, \ldots, A_k} \]
    \end{definition}

@@

    \section{Compatibility, Contextuality and the Marginal Problem}
    \label{sec:comp_con_mp}
    In order to determine if a given marginal distribution $\prob[V]$ or set of marginal distributions $\prob[V_{\bs{k}}] \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ is compatible with a causal structure $\graph$, one should first formalize what is meant by \textit{compatible}.

    \begin{definition}
        A set of \term{causal parameters} for a particular causal structure $\graph$ is the specification of a conditional distribution for every node $n \in \nodes$ given it's parents in $\graph$.
        \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \]
    \end{definition}
    \begin{definition}
        \label{def:compatible}
        A marginal distribution $\prob[V]$ is \term{compatible} with a causal structure $\graph$ (where it is assumed that $V \subseteq \nodes_O$) if there exists a \textit{choice} of causal parameters $\bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes}$ such that $\prob[V]$ can be \textit{recovered} from the following series of operations:
        \begin{enumerate}
            \item First obtain a joint distribution over \textit{all} nodes of of the causal structure,
            \[ \prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] \]
            \item Then marginalize over the latent nodes of $\graph$,
            \[ \prob[\nodes_O] = \sum_{\nodes_L} \prob[\nodes] \]
            \item Finally marginalize over the observed nodes not in $V$ to obtain $\prob[V]$,
            \[ \prob[V] = \sum_{\nodes_O \setminus V} \prob[\nodes_O] \]
        \end{enumerate}
        A set of marginal distributions $\prob[V_{\bs{k}}]$ is compatible with $\graph$ if each of the distributions can be made compatible by the \textit{same} choice of causal parameters.
        A distribution $\prob[V]$ or set of distributions $\prob[V_{\bs{k}}]$ is said to be \term{incompatible} with a causal structure if there \textit{does not exist} a set of causal parameters with the above mentioned property.

        \todo[TC]{Source this?}
    \end{definition}
    Operations 2 and 3 of \cref{def:compatible} are related to the \textit{marginal problem}.
    \begin{definition}
        \label{def:marginal_problem}
        \term{The Marginal Problem:} Given a set of distributions $\prob[V_{\bs{k}}] \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ where $V_i \subseteq \mathcal{V}$ for some set of random variables $\mathcal{V}$ and $k \geq 2$, does there exist a joint distribution $\prob[\mathcal{V}]$ such that each given distribution $\prob[V_i]$ can be obtained from marginalizing $\prob[\mathcal{V}]$?
        \[ \forall i \in \bs{k} : \prob[V_i] = \sum_{\mathcal{V} \setminus V_i} \prob[\mathcal{V}] \]
        Typically (although not strictly necessary), $\mathcal{V}$ is taken to mean the union of all $V_i$'s.
        \[ \mathcal{V} = V_1 \cup \cdots \cup V_k = \bigcup_{i\in\bs{k}} V_i \eq \label{eq:marginals_union} \]
    \end{definition}

    \todo[TC]{Mention polytope perspective and existing methods}
    \begin{definition}
        \label{def:marginal_model}
        A reoccurring motif of these discussions will be the set of distributions $\prob[V_{\bs{k}}] \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ mentioned in \cref{def:marginal_problem}. In agreement with \cite{Fritz_2011} we will call this set of distributions a \term{marginal model} and denote it $\prob_{V_{\bs{k}}}$ provided that they are \textit{compatible}:
        \[ \forall i \neq j \text{ if } V_i \cap V_j \neq \emptyset \text{ then } \sum_{V_i \setminus V_j} \prob[V_i] = \sum_{V_j \setminus V_i} \prob[V_j]  \]
        We call the set of subsets $V_{\bs{k}} \defined \bc{V_1, \ldots, V_k}$ the marginal contexts or the \term{maximal marginal scenario} $V_{\bs{k}}$\footnote{Rigorously speaking as defined by \cite{Fritz_2011}, a marginal scenario forms an \textit{abstract simplicial complex} where $V' \in V_{\bs{k}}$ whenever $V' \subseteq V_i$ for some $i$. ``Maximal'' refers to the restriction that $\forall i,j : V_i \not \subseteq V_j$.} and an individual $V_i$ a \term{marginal context}. The union of all contexts is denoted $\mathcal{V}$ and define it exactly as in \cref{eq:marginals_union}.

        Following definition 2.3 in \cite{Fritz_2011}, a marginal model is said to be \term{contextual} if it \textit{does not} admit a solution to the marginal problem and \term{non-contextual} otherwise.

        In addition, we elect to define the \term{marginal outcomes} $O_{V_{\bs{k}}}$ to be the set of all outcomes belonging to outcomes of the marginal contexts.
        \[ O_{V_{\bs{k}}} \defined O_{V_1} \cup \cdots \cup O_{V_k} = \bigcup_{i \in \bs{k}} O_{V_i} \]
        % By an intended abuse of notation, we say that a particular outcome is an ``element'' of $O_{V_{\bs{k}}}$ if it is an element of $O_{V_i}$ for some $i \in \bs{k}$.
        % \[ \outc{V_i} \in O_{V_{\bs{k}}} \]
        Note that $O_{V_{\bs{k}}}$ is \textit{not} a valid outcome space, analogous to the fact that $P_{V_{\bs{k}}}$ is \textit{not} a probability distribution. Instead $O_{V_{\bs{k}}}$ is a collection of outcome spaces just as $P_{V_{\bs{k}}}$ is a collection of distributions.
    \end{definition}

@@

        A \term{causal compatibility inequality} $\mathcal{I}_{V_{\bs{k}}}$ for a marginal scenario $V_{\bs{k}}$ is a probabilistic inequality that is obeyed for every compatible marginal model $\prob_{V_{\bs{k}}}$. Whenever the marginal scenario $V_{\bs{k}}$ in question is evident by context, the subscript of $\mathcal{I}_{V_{\bs{k}}}$ will be dropped leaving just $\mathcal{I}$.

@@

    \section{Logical Implications of Non-Contextuality}

>>>>

% === Commonly re-occurring symbols ===
\newcommand{\hgraph}{\mathcal{H}}
\newcommand{\graph}{\mathcal{G}}
\newcommand{\nodes}{\mathcal{N}}
\newcommand{\weights}{\mathcal{W}}
\newcommand{\edges}{\mathcal{E}}
\newcommand{\trans}{\mathcal{T}}
\newcommand{\ind}{\mathcal{I}}
\newcommand{\perm}{\Omega}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\ancestralindep}{\perp}
\newcommand{\valprod}{\times}
\newcommand{\bigvalprod}{\prod}
\newcommand{\com}{\mathrel{\Yright\hspace{-0.2em}\Yleft}}
\newcommand{\ext}{\mathrel{\Yright}}
\newcommand{\res}{\mathrel{\Yleft}}
\newcommand{\gelem}{\varphi}
\newcommand{\action}[1]{\gelem\bs{#1}}
\newcommand{\mscenario}{\mathcal{M}}
\newcommand{\jointvar}{\mathcal{J}}
% When I introduce a new term or definition
\newcommand{\term}[1]{\textcolor{Mahogany}{\textbf{#1}}}

% === Mathematical operators that are denoted with words ===
\newcommand{\setoperator}[1]{%
\expandafter\DeclareDocumentCommand\csname#1\endcsname{O{} O{} m}{{\mathsf{#1}_{##1}^{##2}}\br{##3}}%
}

\setoperator{Pa} % Parents of a node
\setoperator{Ch} % Children of a node
\setoperator{An} % Ancestry of a node
\setoperator{Sub} % subgraph
\setoperator{AnSub} % Ancestral subgraph
\setoperator{Ext} % Extension of outcomes
\setoperator{Com} % Compatible equivalence relation
\setoperator{Nec} % Necessary nodes
\setoperator{UnNec} % Unnecessary nodes
\setoperator{Inj} % injectable sets
\setoperator{ImInj} % images of the injectable sets
\setoperator{PreInj} % Pre-injectable sets
\setoperator{Aut} % graph automorphism
\setoperator{Orb} % Group Orbits
\setoperator{Perm} % Permutation group
\setoperator{Out} % Outcome space
\setoperator{Dom} % Domian

\newcommand{\outc}[1]{o\bs{#1}} % Fritz's BBTII notation for observed outcomes
\DeclareDocumentCommand{\prob}{O{} O{}}{\ifthenelse{\equal{#1}{}}{P}{P_{#1}}\ifthenelse{\equal{#2}{}}{}{\br{#2}}} % probability distribution
\DeclareDocumentCommand{\probvec}{O{} O{}}{\ifthenelse{\equal{#1}{}}{\mathcal{P}}{\mathcal{P}_{#1}}\ifthenelse{\equal{#2}{}}{}{\br{#2}}} % probability distribution vector

@@

    \section{Introduction}
    \todo[TC]{Discuss why the marginal problem is important.}
    \section{Definitions \& Notation}
    \comment[TC]{This entire section should be integrated into the body when logical to do so.}
    \begin{definition}
        Following common notation used in \cite{Fritz_2011}, we use the notation $\bs{k} = \bc{1, \ldots, k}$ to be a finite index set. Moreover, when referencing a finite set with $k$ elements, we can write,
        \[ A_{\bs{k}} \defined \bc{A_i}_{i \in \bs{k}} = \bc{A_1, \ldots, A_k} \]
    \end{definition}
    \begin{definition}
        \label{def:outcome_space}
        Each random variable $v$ has a set of possible outcomes which are labeled by \term{outcome labels} $O_v$. The set of all outcomes themselves is its \term{outcome space} and is represented by the set of all functions from $v$ to $O_v$\footnote{Using functional language for outcome events is necessary for a sheaf-theoretic treatment of contextuality \cite{Abramsky_2011}.},
        \[ \Out{v} \defined \bc{f : \bc{v} \to O_v} \]
        Each of these functions has a singular domain ($v$) and thus can be concisely written in a compact form $\bc{v \mapsto o}$ where $o \in O_v$ represents some generic outcome label. Each function $f$ should be interpreted as the \textit{event} that $v$ obtains the outcome $o$, as well as the function that takes $v$ to $o$ $\bc{v \mapsto f\br{v} = o}$. Evidently $\Out{v}$ is isomorphic to $O_v$, and in many cases the two can be considered equivalent; however we make this particular semantic distinction now in preparation of \cref{sec:symmetry}.
    \end{definition}

    \begin{definition}
        This notation generalizes to more than one variable. Letting $V = \bc{v_1, v_2}$, we define $\Out{V}$ to be the set of all joint valuations of $v_1$ and $v_2$.
        % Where the valuation product between outcome spaces is defined as follows,\footnote{At this level, a valuation product behaves analogously to a Cartesian product. However in \cref{def:extendable_set}, we define the a valuation product between outcomes and outcomes spaces.}
        \[ \Out{V} = \Out{\bc{v_1, v_2}} \defined \bc{f : \bc{v_1, v_2} \to \bc{O_{v_1}, O_{v_2}} \mid f\br{v_i} \in O_{v_i}, i \in \bc{1,2}}  \]
        As a natural generalization, when considering a larger set of random variables $V = \bc{v_i}_{i \in \bs{k}}$ we define the joint outcome space in an analogous way,
        \[ \Out{V} \defined \bc{f: \bc{v_i}_{i \in \bs{k}} \to \bc{O_{v_i}}_{i \in \bs{k}} \mid \forall i \in \bs{k} : f\br{v_i} \in O_{v_i} } \eq \label{eq:outcome_space}\]
        Each outcome $f$ can be compactly represented as a set of mappings over each element of $V$.
        \[ f = \bc{v_1 \mapsto f\br{v_1}, \ldots, v_k \mapsto f\br{v_k}} = \bc{v_i\mapsto f\br{v_i}}_{i \in \bs{k}} \]
        The domain of $f$ refers to the set of random variables it valuates and is denoted as $\Dom{f}$. If $f \in \Out{V}$, then $\Dom{f} = V$.
        % Where the joint outcome labels are elements of a Cartesian product,
        % \[ O_V \defined O_{v_1} \times \cdots \times O_{v_{\abs{V}}}  \]

        % And a generic, unspecified joint outcome in $\Out{V}$ is written as $\outc{V}$ in a similar fashion to \cref{def:outcome_space} and is represented by a tuple of individual outcomes.
        % \[ \outc{V} \defined \br{\outc{v_1}, \ldots, \outc{v_{k}}} = \br{\outc{v}}_{v \in V} \eq \label{eq:outcomespace}\]
        % It is important to note that the ordering of events in \cref{eq:outcomespace} is irrelevant.
         % The definition of a valuation product can also be extended to outcomes themselves. Let $A$ and $B$ be sets of random variables and let $\outc{A} \in \Out{A}$ and $\outc{B} \in \Out{B}$. If $$
    \end{definition}

    \begin{example}
        Interpreting $f \in \Out{V}$ as an \textit{event} or \textit{outcome} on $V$, a probability distribution $\prob[V]$ over $V$ will assign a non-negative probability $\prob[V][f]$ to $f$. Let $V = \bc{v_1, v_2}$ with each $v \in V$ having $3$ distinct outcomes $O_v = \bc{0,1,2}$. Furthermore let $f \in \Out{V}$ be the outcome $\br{v_1 \mapsto 2, v_2 \mapsto 1}$. The following class of notations will be considered interchangeable,
        \[ \prob[V][f] = \prob[v_1, v_2][f] = \prob[][v_1 \mapsto f_1\br{v_1}, v_2 \mapsto f_2\br{v_2}] = \prob[][v_1 \mapsto 2, v_2 \mapsto 1] = \prob[v_1v_2][21] \]
        Each of which should be read as ``the probability that $v_1$ gets outcome $2$ AND $v_2$ gets outcome $1$''.
    \end{example}

    \begin{remark}
        \label{rem:domain_dist}
        In each of the above notations, $\prob[V]$ always represents a probability distribution over the \textit{domain} of $f \in \Out{V}$. In cases where the subscript is omitted, it should be assumed to be over the domain of $f$.
        \[ \prob[V][f] = \prob[\Dom{f}][f] = \prob[][f] \]
    \end{remark}

    \begin{definition}
        \label{def:restriction}
        Let $V = \bc{v_1, \ldots, v_k}$ be a set of random variables and $W \subseteq V$ be a subset of $V$. Moreover, let $f \in \Out{V}$ be a joint outcome over $V$; assigning a unique label to each variable in $V$. The \term{restriction of $f$ onto $W$} (denoted $f|_{W} \in \Out{W}$) is the outcome of $\Out{W}$ that \textit{agrees} with each of $f$'s assignments for variables in $W$.
        \[ \forall v \in W : f\br{v} = f|_{W}\br{v} \]
    \end{definition}

    \begin{definition}
        \label{def:outcome_compatible}
        Consider two sets of random variables $V$ and $W$ and two specific outcomes $f_V \in \Out{V}$ and $f_W \in \Out{W}$. The outcomes $f_V$ and $f_W$ are said to be \term{compatible} if they agree on their valuations of $V \cap W$. Compatibility will be denoted with `$\com$'.
        \[ f_V \com f_W \iff {f_V}|_{V\cap W} = {f_W}|_{V\cap W} \]
        Compatibility is a reflexive and symmetric, but \textit{not} transitive. There are two cases when compatibility is transitive; whenever $V \cap W = \emptyset$ or $V = W$. Whenever $V \cap W = \emptyset$, $f_V$ and $f_W$ can be said to be \textit{trivially} compatible. Moreover if $V = W$, compatibility becomes ordinary equivalence,
        \[ V = W \quad \textrm{and} \quad f_V \com f_W \iff f_V = f_W \]
    \end{definition}

    \begin{definition}
        \label{def:extendable}
        Let $f_V \in \Out{V}$ and $f_W \in \Out{W}$ be outcomes of $V$ and $W$ respectively as in \cref{def:outcome_compatible}. If $f_V$ and $f_W$ are compatible, and $W \subseteq V$ then $f_W$ is said to be \term{extendable} to $f_V$ and is denoted `$\ext$'.
        \[ f_W \ext f_V \iff f_W \com f_V \quad \textrm{and} \quad W \subseteq V \iff {f_W} = {f_V}|_{W} \]
        The dual language is also appropriate: $f_W$ is a \term{restriction} of $f_V$ (denoted $f_V \res f_W$) if and only if $f_W$ is extendable to $f_V$. If $f_W \ext f_V$ then there exists a unique element $f_{V \setminus W} \in \Out{V \setminus W}$ such that $f_V$ can be reconstructed by gluing together $f_{V \setminus W}$ and $f_W$.
        \[ \forall v \in V : f_V\br{v} = \begin{cases}
            f_W\br{v} & v \in W \\
            f_{V\setminus W}\br{v} & v \in V \setminus W
        \end{cases}  \]
    \end{definition}

    \begin{remark}
        The notation `$g \com h$' is used to indicate compatibility between $g \in \Out{V}$ and $h \in \Out{W}$ because of the following observation; $g$ and $h$ are compatible if and only if they are extendable to some outcome $f \in \Out{V \cup W}$.
        \[ g \com h \iff \exists f \in \Out{V \cup W} \mid g \ext f \res h \]
        In fact, such an $f$ is uniquely defined,
        \[ \forall v \in V : f\br{v} = \begin{cases}
            g\br{v} & v \in V \\
            h\br{v} & v \in W
        \end{cases} \]
    \end{remark}

    \begin{definition}
        \label{def:extendable_set}
        The set of all extendable outcomes of $f \in \Out{W}$ into $V$ is called the \term{extendable set of $f$ into $V$} and can be written as,
        \[ \Ext[V]{f} \defined \bc{g \in \Out{V} \mid f \ext g} \subseteq \Out{V} \]
        The extendable set of $f$ into $V$ is the subset of outcomes in $\Out{V}$ that \textit{agree} with $f$ about valuations for variables in $W$.
    \end{definition}

    \begin{example}
        Let $W = \bc{a, b}$ and $V = \bc{a, b, c}$ be two sets of random variables. Clearly $W \subseteq V$; a prerequisite for extendability. Further impose that the outcome labels for each variable are the same: $O_a = O_b = O_c = \bc{0,1,2}$. As an example, let $f = \bc{a \mapsto f\br{a} = 1, b \mapsto f\br{b} = 2} \in \Out{W}$; $f$ is extendable to the outcome $g = \bc{a \mapsto g\br{a} = 1, b \mapsto g\br{b} = 2, c \mapsto g\br{c} = 1} \in \Out{V}$, and the extendable set of $f$ into $V$ is,
        \[ \Ext[V]{f} = \Ext[a,b,c]{a \mapsto 1, b \mapsto 2} = \bc{\bc{a \mapsto 1, b \mapsto 2, c \mapsto 0}, \bc{a \mapsto 1, b \mapsto 2, c \mapsto 1}, \bc{a \mapsto 1, b \mapsto 2, c \mapsto 2}} \]
    \end{example}

@@

    \begin{definition}
        The \term{product distribution} of two disjoint distributions $\prob[V]$ and $\prob[W]$ (where $V \cap W = \emptyset$) is denoted as usual with $\prob[V] \times \prob[W]$ and is defined as,
        \[ \forall f \in \Out{V \cup W} : \br{\prob[V] \times \prob[W]}\br{f} \defined \prob[V][f|_{V}]\cdot\prob[W][f|_{W}] \]
        A product distribution of $k$ mutually disjoint distributions is defined as,
        \[ \prod_{i\in\bs{k}} \prob[V_i] \defined \br{\prob[V_1] \times \cdots \times \prob[V_k]} \]
    \end{definition}

    \begin{definition}
        The \term{marginalization} of a distribution $\prob[V]$ to a distribution over $W \subseteq V$ is denoted $\sum_{V \setminus W} \prob[V]$ and is defined such that,
        \[ \forall f \in \Out{W} : \br{\sum_{V \setminus W} \prob[V]}\br{f} \defined \sum_{g \in \Ext[V]{f}} \prob[V][g] \]
    \end{definition}

@@

    \section{Compatibility, Contextuality and the Marginal Problem}
    \label{sec:comp_con_mp}
    In order to determine if a given marginal distribution $\prob[V]$ or set of marginal distributions $\bc{\prob[V_i]}_{i \in \bs{k}} \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ is compatible with a causal structure $\graph$, one should first formalize what is meant by \textit{compatible}.

    \begin{definition}
        A set of \term{causal parameters} for a particular causal structure $\graph$ is the specification of a conditional distribution for every node $n \in \nodes$ given it's parents in $\graph$.
        \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \]
    \end{definition}
    \begin{definition}
        \label{def:compatible}
        A marginal distribution $\prob[V]$ is \term{compatible} with a causal structure $\graph$ (where it is assumed that $V \subseteq \nodes_O$) if there exists a \textit{choice} of causal parameters $\bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes}$ such that $\prob[V]$ can be \textit{recovered} from the following series of operations:
        \begin{enumerate}
            \item First obtain a joint distribution over \textit{all} nodes of of the causal structure,
            \[ \prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] \]
            \item Then marginalize over the latent nodes of $\graph$,
            \[ \prob[\nodes_O] = \sum_{\nodes_L} \prob[\nodes] \]
            \item Finally marginalize over the observed nodes not in $V$ to obtain $\prob[V]$,
            \[ \prob[V] = \sum_{\nodes_O \setminus V} \prob[\nodes_O] \]
        \end{enumerate}
        A set of marginal distributions $\bc{\prob[V_{i}]}_{i \in \bs{k}}$ is compatible with $\graph$ if each distribution $\prob[V_{i}]$ can be made compatible by the \textit{same} choice of causal parameters.
        A distribution $\prob[V]$ or set of distributions $\bc{\prob[V_{i}]}_{i \in \bs{k}}$ is said to be \term{incompatible} with a causal structure if there \textit{does not exist} a set of causal parameters with the above mentioned property.

        \todo[TC]{Source this?}
    \end{definition}
    Operations 2 and 3 of \cref{def:compatible} are related to the \textit{marginal problem}.
    \begin{definition}
        \label{def:marginal_problem}
        \term{The Marginal Problem:} Given a set of distributions $\bc{\prob[V_{i}]}_{i \in \bs{k}} \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ where $V_i \subseteq \jointvar$ for some set of random variables $\jointvar$, does there exist a joint distribution $\prob[\jointvar]$ such that each given distribution $\prob[V_i]$ can be obtained from marginalizing $\prob[\jointvar]$?
        \[ \forall i \in \bs{k} : \prob[V_i] = \sum_{\jointvar \setminus V_i} \prob[\jointvar] \]
        Typically (although not strictly necessary\footnote{Appending any additional variables to $\jointvar$ will not affect the existence of a joint distribution.}), $\jointvar$ is taken to mean the union of all $V_i$'s.
        \[ \jointvar = V_1 \cup \cdots \cup V_k = \bigcup_{i\in\bs{k}} V_i \eq \label{eq:marginals_union} \]
    \end{definition}

    \todo[TC]{Mention polytope perspective and existing methods}
    \begin{definition}
        \label{def:marginal_model}
        A reoccurring motif of these discussions will be the set of distributions $\bc{\prob[V_{i}]}_{i \in \bs{k}} \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ mentioned in \cref{def:marginal_problem}. In agreement with \cite{Fritz_2011} we call the set of subsets $\mscenario \defined \bc{V_1, \ldots, V_k}$ the marginal contexts or the \term{maximal marginal scenario}\footnote{Rigorously speaking as defined by \cite{Fritz_2011}, a marginal scenario forms an \textit{abstract simplicial complex} where it is required that $V' \in \mscenario$ whenever $V' \subseteq V_i$ for some $i \in \bs{k}$. ``Maximal'' refers to the restriction that $\forall i,j : V_i \not \subseteq V_j$.}. An individual $V_i \in \mscenario$ is a \term{marginal context}. The union of all contexts is denoted $\jointvar$ and is defined exactly as in \cref{eq:marginals_union}.
        Moreover, we will call the set of distributions a \term{marginal model} and denote it $\prob^{\mscenario}$ provided that they are \textit{compatible} \todo[TC]{Mention quantum non-signalling and maybe $k \geq 3$}:
        \[ \forall i \neq j \text{ if } V_i \cap V_j \neq \emptyset \text{ then } \sum_{V_i \setminus V_j} \prob[V_i] = \sum_{V_j \setminus V_i} \prob[V_j]  \]
        Following definition 2.3 in \cite{Fritz_2011}, a marginal model is said to be \term{contextual} if it \textit{does not} admit a joint distribution $\prob[\jointvar]$ and \term{non-contextual} otherwise.

        In addition, we elect to define the \term{marginal outcomes} $\Out{\mscenario}$ to be the set of all outcomes belonging to outcomes $\Out{V_i}$ of the marginal context\footnote{Here `$\coprod$' refers to the \textit{disjoint union} of outcome contexts; when $i \neq j$, $\Out{V_i} \cap \Out{V_j} = \emptyset$ since $V_i \neq V_j$.}.
        \[ \Out{\mscenario} \defined \coprod_{i \in \bs{k}} \Out{V_i} \]
        % By an intended abuse of notation, we say that a particular outcome is an ``element'' of $O_{\mscenario}$ if it is an element of $O_{V_i}$ for some $i \in \bs{k}$.
        % \[ \outc{V_i} \in O_{\mscenario} \]
        Each marginal outcome $m \in \Out{\mscenario}$ belongs to a unique marginal outcome space $\Out{V_i}$. To make reference to the marginal context $V_i$ associated with $m$, recall \cref{rem:domain_dist}: the context for $m$ is precisely the domain of $m$ ($V_i = \Dom{m}$). Note that $\Out{\mscenario}$ is a slight abuse of notation; $\Out{\mscenario}$ is \textit{not} a valid outcome space, analogous to the fact that $P^{\mscenario}$ is \textit{not} a probability distribution. Instead $\Out{\mscenario}$ is a \textit{flattened} collection of outcome spaces just as $P^{\mscenario}$ is a collection of distributions. The \term{joint outcomes} $\Out{\jointvar}$ are defined in the usual fashion of \cref{def:outcome_space}.
    \end{definition}

@@

        A \term{causal compatibility inequality} $\mathcal{I}_{\mscenario}$ for a marginal scenario $\mscenario$ is a probabilistic inequality that is obeyed for every compatible marginal model $\prob^{\mscenario}$. Whenever the marginal scenario $\mscenario$ in question is evident by context, the subscript of $\mathcal{I}_{\mscenario}$ will be dropped leaving just $\mathcal{I}$.

@@

    \section{Covering Inequalities}
